Code for Graphs for ASN presentation

### 2020-12-17 ASNCode.Rmd
Changed graphs to 3 outcomes, rather than 4. Changed colors, added wasp graph

```{r}
data <- read.csv("~/Desktop/MsCcHSFeedNov30modfinal.csv")
scan <- read.csv("~/Desktop/MsCcHSFeedLeafScanFinal.csv", header = T)
```

@@

```{r}
data <- data[data$fate != "dead" & data$fate != "quink" & data$fate != "wander*" & data$fate != "?", ]
```

@@

@@

Four colors I'm using:

emerged: #66CB5D
wander: #21908D
wowe: #3E4F8A
wowe mongo: #450D54

@@

@@

```{r}
ggplot(aes(x = ttmax, y = mass.max, color = fate), data = DCdata) +
  theme_bw() + 
  geom_point(alpha = 0.8) + 
  scale_color_manual(values = c("#66CB5D", "#21908D", "#3E4F8A", "#450D54")) + 
  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (mg)", 
       color = "Developmental Outcome")
```

@@

```{r}
ggplot(aes(x = area, y = mass.max), data = DCdata) + 
  theme_bw() + 
  geom_point(aes(color = fate)) + 
  scale_color_manual(values = c("#66CB5D", "#21908D", "#3E4F8A", "#450D54")) +
  labs(x = "Leaf surface area consumed (cm2)", y = "Maximum mass achieved (mg)",
       color = "Developmental Outcome")
```
```{r}

>>>>

```{r}
data <- read.csv("~/Desktop/MsCcHSFeedDec14final.csv")
scan <- read.csv("~/Desktop/MsCcHSFeedLeafScanFinal.csv", header = T)
```

@@

```{r}
data <- data[data$fate != "dead" & data$fate != "quink" & data$fate != "wander*" & data$fate != "?", ]

data$outcome <- data$fate

data$outcome <- gsub(" mongo", "", data$outcome)
data$outcome <- gsub("em", "we", data$outcome)

@@

```{r}
data$perc.w.ecl <- data$num.w.eclos / (data$num.w.coc + data$num.w.larvae)
data$num.w.total <- (data$num.w.coc + data$num.w.larvae)

data$HS <- factor(data$HS, levels = c("yes", "no"))
```

@@

Three colors I'm using:

("#66CB5D", "#21908D", "#3E4F8A", "#450D54")
("#460F5A", "#87D548", "#30B67B")

wander: #882255
we: #88CCEE
wowe: #117733

@@

```{r}
ggplot(aes(x = num.w.total, y = perc.w.ecl, color = HS), data = data) + 
  theme_bw() + 
  geom_smooth(method = "lm", se = F) +
  geom_point(alpha = 0.8, aes(shape = food)) + 
  scale_shape_manual(values = c(19, 6)) +
  scale_color_manual(values = c("#EF000D", "#00CFD2")) + 
  labs(x = "Number of wasps emerged", y = "Percentage of wasps eclosed", shape = "Hostplant Consumed", 
       color = "Heat Shock Status")
```

@@

```{r}
ggplot(aes(x = ttmax, y = mass.max, color = outcome, shape = food), data = data) +
  theme_bw() + 
  geom_point(alpha = 0.8) + 
  scale_shape_manual(values = c(19, 6)) + 
  scale_color_manual(values = c("#882255", "#88CCEE", "#117733")) + 
  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (mg)", 
       color = "Developmental Outcome", shape = "Hostplant Consumed")
```

@@

```{r}
ggplot(aes(x = area, y = mass.max), data = data) + 
  theme_bw() + 
  geom_point(aes(color = outcome, shape = food)) + 
  scale_shape_manual(values = c(19, 6)) + 
  scale_color_manual(values = c("#882255", "#88CCEE", "#117733")) +
  labs(x = "Leaf surface area consumed (cm2)", y = "Maximum mass achieved (mg)",
       color = "Developmental Outcome", shape = "Hostplant Consumed")
```
